An elaborate data set on human gait and the effect of mechanical perturbations

### 2015-03-04 paper.tex
treadmill > treadmill base, fixes #127.

The acceleration of the treadmill was measured during each trial by four
ADXL330 accelerometers placed at the four corners of the machine. These
accelerometers were intended to provide information for inertial compensation
purposes when the treadmill moved laterally or in pitch, but are extraneous for
trials greater than number 8 due to the treadmill being stabilized in those
degrees of freedom.
%
\begin{figure}
  \centering
  \includegraphics{figures/treadmill.png}
  \caption{The treadmill with coordinate system, cameras (circled in orange),
    projection screen, and safety rope. The direction of travel is in the $-z$
    direction.}
  \label{fig:treadmill}
\end{figure}

@@

After obtaining informed consent and a briefing by the experimentalist on the
trial protocol, the subject followed the verbal instructions of the
experimentalist and the on-screen instructions from the video display. The
protocol for a single trial was as follows:
%
\begin{enumerate}
  \item Subject stepped onto the treadmill and markers were identified with
    Cortex.
  \item The safety rope was attached loosely to the rock climbing harness such
    that no undue forces were acting on the subject during walking, but that
    the harness would prevent a full fall.
  \item The subject started by stepping on sides of treadmill so that feet did
    not touch the force plates and the force plate signals are zeroed. This
    corresponds to the ``Force Plate Zeroing'' event.
  \item Once notified by the video display, the subject stood in the
    initialization pose: standing straight up, looking forward, arms out by
    their sides (~45 degrees) and the event, ``Calibration Pose'', was manually
    recorded by the operator.
  \item A countdown to the first normal walking phase was displayed. At the end
    of the countdown the event ``First Normal Walking'' was recorded and the
    treadmill ramped up to the specified speed and the subject was instructed
    to walk normally, to focus on the ``endless'' road on the display, and not
    to look at their feet.
  \item After 1 minute of normal walking, the longitudinal perturbation phase
    begun and was recorded as ``Longitudinal Perturbation''.
  \item After 8 minutes of walking under the influence of the perturbations,
    the second normal walking phase begun and was recorded as ``Second Normal
    Walking''.
  \item After 1 minute of normal walking, a countdown was shown on the display
    and the treadmill decelerated to a stop.
  \item The subject was instructed to step off of the force plates for 10
    seconds and the ``Unloaded End'' event was recorded.
  \item The subject could then take a rest break before each additional trial.
\end{enumerate}

@@

    F   & 14 & LLEE  & Left lateral elbow                    & Left lateral epicondyle of the elbow. Upper one in the T-Pose. \\
    F   & 15 & LMEE  & Left medial elbow                     & Left medial epicondyle of the elbow. Lower on in the T-Pose. \\

@@

    F   & 22 & RLEE  & Right lateral elbow                   & Right lateral epicondyle of the elbow. Lower one in the T-pose. \\
    F   & 23 & RMEE  & Right medial elbow                    & Right medial epicondyle of the elbow. Lower one in the T-pose. \\

@@

A similar work flow was used to produce Figure~\ref{fig:angle-torque-comparison}
which compares the mean and standard deviation of sagittal plane joint angles
and torques from the perturbed gait cycles and the unperturbed gait cycles
computed from trial 20. This gives an idea of the more highly variable dynamics
required to walk while being longitudinally perturbed.
%
\begin{figure}
  \centering
  \includegraphics{figures/unperturbed-perturbed-comparison.pdf}
  \cprotect\caption{Right leg mean and $3\sigma$ (shaded) joint angles and
    torques from both unperturbed (red) and perturbed (blue) gait cycles
    from trial 20. Produced by \verb|src/unperturbed_perturbed_comparison.py|.}
  \label{fig:angle-torque-comparison}
\end{figure}

>>>>

The acceleration of the treadmill base was measured during each trial by four
ADXL330 accelerometers placed at the four corners of the machine. These
accelerometers were intended to provide information for inertial compensation
purposes when the treadmill moved laterally or in pitch, but are extraneous for
trials greater than number 8 due to the treadmill being stabilized in those
degrees of freedom.
%
\begin{figure}
  \centering
  \includegraphics{figures/treadmill.png}
  \caption{The treadmill with coordinate system, cameras (circled in orange),
    projection screen, and safety rope. The direction of travel is in the $-z$
    direction.}
  \label{fig:treadmill}
\end{figure}

@@

After obtaining informed consent and a briefing by the experimentalist on the
trial protocol, the subject followed the verbal instructions of the
experimentalist and the on-screen instructions from the video display. The
protocol for a single trial was as follows:
%
\begin{enumerate}
  \item Subject stepped onto the treadmill and markers were identified with
    Cortex.
  \item The safety rope was attached loosely to the rock climbing harness such
    that no undue forces were acting on the subject during walking, but that
    the harness would prevent a full fall.
  \item The subject started by stepping on sides of treadmill so that feet did
    not touch the force plates and the force plate signals are zeroed. This
    corresponds to the ``Force Plate Zeroing'' event.
  \item Once notified by the video display, the subject stood in the
    calibration pose: standing straight up, looking forward, arms out by their
    sides (approximately 45 degree abduction) and the event, ``Calibration
    Pose'', was manually recorded by the operator.
  \item A countdown to the first normal walking phase was displayed. At the end
    of the countdown the event ``First Normal Walking'' was recorded and the
    treadmill ramped up to the specified speed and the subject was instructed
    to walk normally, to focus on the ``endless'' road on the display, and not
    to look at their feet.
  \item After 1 minute of normal walking, the longitudinal perturbation phase
    begun and was recorded as ``Longitudinal Perturbation''.
  \item After 8 minutes of walking under the influence of the perturbations,
    the second normal walking phase begun and was recorded as ``Second Normal
    Walking''.
  \item After 1 minute of normal walking, a countdown was shown on the display
    and the treadmill decelerated to a stop.
  \item The subject was instructed to step off of the force plates for 10
    seconds and the ``Unloaded End'' event was recorded.
  \item The subject could then take a rest break before each additional trial.
\end{enumerate}

@@

    F   & 14 & LLEE  & Left lateral elbow                    & Left lateral epicondyle of the elbow. \\
    F   & 15 & LMEE  & Left medial elbow                     & Left medial epicondyle of the elbow. \\

@@

    F   & 22 & RLEE  & Right lateral elbow                   & Right lateral epicondyle of the elbow. \\
    F   & 23 & RMEE  & Right medial elbow                    & Right medial epicondyle of the elbow. \\

@@

A similar work flow was used to produce Figure~\ref{fig:angle-torque-comparison}
which compares the mean and standard deviation of sagittal plane joint angles
and torques from the perturbed gait cycles and the unperturbed gait cycles
computed from trial 20. This gives an idea of the more highly variable dynamics
required to walk while being longitudinally perturbed.
%
\begin{figure}
  \centering
  \includegraphics{figures/unperturbed-perturbed-comparison.pdf}
  \cprotect\caption{Right leg mean and $3\sigma$ (shaded) joint angles and
    torques from both unperturbed (red) and perturbed (blue) gait cycles
    from trial 20. We define the nominal configuration, i.e. all joint angles
    equal to zero, such that the vectors from the shoulder to the hip, the hip
    to the knee, the knee to the ankle, and the heel to the toe are all aligned.
    Produced by \verb|src/unperturbed_perturbed_comparison.py|.}
  \label{fig:angle-torque-comparison}
\end{figure}
